### 2014-02-14 paper/cesk.tex
send/recv

>>>>

\Red{ds: Should we consider the case where the state is shared among
threads? If so, then we need to actually give an SOS condition. For
Browbound we don't need this because this model would correspond to
the event loop and we have our threads running with different global;
of course message handlers do share state, but we can handle this case
without changes (I think)}
